Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-19 doc/leanappendix.tex
One more Lean data point
Final data
Change explanation
Final Lean data point

As would be expected, the \lean{} checker consistently runs slower
than the unverified checker.  Two of the benchmarks exceeded the time
limit of 1000 seconds with the \lean{} checker.  Of those that
completed, the ratio of the runtime for \lean{} versus the runtime for
the unverified checker had a harmonic mean of 5.9.

Importantly, however, it can be seen that both checkers show the same
overall asymptotic performance.  The ratio of the two runtimes was
less than $8.0$ for all but two very small benchmarks.  This seems like a
reasonable price to pay for a rigorous guarantee of correctness.

>>>>

As would be expected, the \lean{} checker consistently runs slower
than the unverified checker.  All of the checks completed and confirmed the outcome of the unverified checker.
The ratio of the runtime for \lean{} versus the runtime for
the unverified checker had a harmonic mean of $5.94$.

Importantly, however, it can be seen that both checkers show the same
overall performance trends.  The ratio of the two runtimes was less
than $8.0$ for all but three small benchmarks.  This seems like a
reasonable price to pay for a rigorous guarantee of correctness, and
we are confident that we can reduce this gap with more effort in
optimizing the checker.
